xwMOOC 딥러닝

### 2018-05-17 microsoft-azure.Rmd
remove theme journal

---
layout: page
title: xwMOOC 딥러닝
subtitle: 마이크로소프트 애저(Azure)
output:
  html_document: 
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: false
mainfont: NanumGothic
---

>>>>

---
layout: page
title: xwMOOC 딥러닝
subtitle: 마이크로소프트 애저(Azure)
output:
  html_document: 
    toc: yes
    toc_depth: 2
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: false
mainfont: NanumGothic
---
